Lessons Learned for JWST Transiting Planet Time Series from Ground-based Studies of the NIRCam Detectors

### 2019-02-20 ms.tex
labeled phot and spec apertures

We also assume that each read/frame is statistically independent from the other.
We assume therefore the read noise per integration is:
\begin{equation}
RN_{ap,70,75,100} = \frac{21,200 DN}{ \sqrt{N_{frames}}} \approx \frac{46,000 e^-}{ \sqrt{N_{frames}}}
\end{equation},
where $N_{frames}$ is the number of frames in an integration and a gain of 2.17 $e^-$/DN is assumed for the detector.
If there are 2 frames in an integration, we recover 15,000 DN for the case of a read pair subtraction on the A3 detector.
\textcolor{red}{\bf Make sure I scaled this correctly both for the read pair subtraction and a slope fit. Also verify with a slope fit to multiple images.}
For an integration that fills to a peak of $\sim$ 60\% or 35,000 DN, the integrated DN counts would be 10$^8$ DN, having a photon uncertainty of 9,100 DN or 110 ppm.
Therefore, the correlated read noise, if left uncorrected, will have a highly significant ($>50\%$) impact on an integration of 5 or fewer frames.

>>>>

We also assume that each read/frame is statistically independent from the other.
We assume therefore the read noise per integration is:
\begin{equation}
RN_{ap,70,75,100} = \frac{21,200 DN}{ \sqrt{N_{frames}}} \approx \frac{46,000 e^-}{ \sqrt{N_{frames}}}
\end{equation},
where $N_{frames}$ is the number of frames in an integration and a gain of 2.17 $e^-$/DN is assumed for the detector.
If there are 2 frames in an integration, we recover 15,000 DN for the case of a read pair subtraction on the A3 detector.
\textcolor{red}{\bf Make sure I scaled this correctly both for the read pair subtraction and a slope fit. Also verify with a slope fit to multiple images.}
For an integration that fills to a peak of $\sim$ 60\% well depth or 35,000 DN, the integrated DN counts for a WEAK LENS +8 PSF would be 10$^8$ DN, having a photon uncertainty of 9,100 DN or 110 ppm.
Therefore, the correlated read noise, if left uncorrected, will have a highly significant ($>50\%$) impact on an integration of 5 or fewer frames.
